Outbreak Threshold Detection

### 2023-03-06 notebooks/Julia/simulation-detection.qmd
Update infection class notation Change from Keeling and Rohani notation of X/Y/Z to S/I/R with lowercase to denote proportions, as find it easier to add categories with relevant labels - will be useful with latent, vaccinated classes etc

```{julia}
function rate(out, u, p, t)
    out[1] = p[1] * u[1] * u[2] / u[4]      # β * X * Y / N
    out[2] = p[2] * u[2]                    # ν * Y
    out[3] = p[3] * u[4]                    # μ * N
    out[4] = p[3] * u[1]                    # μ * X
    out[5] = p[3] * u[2]                    # μ * Y
    out[6] = p[3] * u[3]                    # μ * Z
    nothing
end
```

```{julia}
c = zeros(4, 6)
# X + Y --> Y
c[1, 1] = -1        # X -> X - 1
c[2, 1] = 1         # Y -> Y + 1

# Y --> Z
c[2, 2] = -1        # Y -> Y - 1
c[3, 2] = 1         # Z -> Z + 1

# X --> 2X
c[1, 3] = 1         # X -> X + 1
c[4, 3] = 1         # N -> N + 1

# X --> 0X
c[1, 4] = -1        # X -> X - 1
c[4, 4] = -1        # N -> N - 1

# Y --> 0Y
c[2, 5] = -1        # Y -> Y - 1
c[4, 5] = -1        # N -> N - 1

# Z --> 0Z
c[3, 6] = -1        # Z -> Z - 1
c[4, 6] = -1        # N -> N - 1

@@

```{julia}
rj = RegularJump(rate, change!, 6)
```

```{julia}
tmax = 250.0
δt = 0.001
tspan = (0.0, tmax)
tlength = length(tspan[1]:δt:tspan[2])
Random.seed!(1234);
```

```{julia}
R₀ = 16
γ = 1/8
μ = 1 / (365 * 62.5)
β = R₀ * (γ + μ)
p = (β, γ, μ)

u₀ = [800, 20, 800, NaN]
u₀[4] = sum(u₀[1:3])
```

```{julia}
prob = DiscreteProblem(u₀, tspan, p)
jump_prob = JumpProblem(prob, Direct(), rj)
sol = solve(jump_prob, TauLeaping(); dt = δt)
sol_array = zeros(5, length(sol))
sol_array[1:4, :] = Array(sol)
sol_array[5, :] = sum(sol_array[1:3, :], dims = 1);

sol_array[4, :] == sol_array[5, :]
```

@@

lines!(ax, sol.t, sol_array[1, :], linewidth = 3, label = "X(t)")
lines!(ax, sol.t, sol_array[2, :], linewidth = 3, label = "Y(t)")
lines!(ax, sol.t, sol_array[3, :], linewidth = 3, label = "Z(t)")
lines!(ax, sol.t, sol_array[4, :], linewidth = 3, label = "N(t) jump")
lines!(ax, sol.t, sol_array[5, :], linewidth = 3, label = "N(t) calc")

>>>>

```{julia}
function rate(out, u, p, t)
    out[1] = p[1] * u[1] * u[2] / (u[1] + u[2] + u[3])           # β * S * I
    out[2] = p[2] * u[2]                      # ν * I
    # out[3] = p[3] * u[1]                    # μ * N
    # out[4] = p[3] * u[1]                    # μ * S
    # out[5] = p[3] * u[2]                    # μ * I
    # out[6] = p[3] * u[3]                    # μ * R
    nothing
end
```

```{julia}
c = zeros(3, 2)
# S + I --> I
c[1, 1] = -1        # S -> S - 1
c[2, 1] = 1         # I -> I + 1

# I --> R
c[2, 2] = -1        # I -> I - 1
c[3, 2] = 1         # R -> R + 1

# S --> 2X
# c[1, 3] = 1         # S -> S + 1

# # S --> 0X
# c[1, 4] = -1        # S -> S - 1

# # I --> 0Y
# c[2, 5] = -1        # I -> I - 1

# # R --> 0Z
# c[3, 6] = -1        # R -> R - 1

@@

```{julia}
rj = RegularJump(rate, change!, 2)
```

```{julia}
tmax = 100.0
δt = 0.001
tspan = (0.0, tmax)
tlength = length(tspan[1]:δt:tspan[2])
Random.seed!(1234);
```

```{julia}
# R₀ = 2
# γ = 1/8
μ = 0.001
# β = R₀ * (γ + μ)
# ζ = 0.001
# p = (β, γ, μ, ζ)

u₀ = [1000.0, 50.0, 0.0]

β = 0.1/1000.0
γ = 0.01
μ = 0.001
p = (β, γ, μ)

```

```{julia}
prob = DiscreteProblem(u₀, tspan, p)
jump_prob = JumpProblem(prob, Direct(), rj)
sol = solve(jump_prob, TauLeaping(); dt = δt)
sol_array = zeros(4, length(sol))
sol_array[1:3, :] = Array(sol)
sol_array[4, :] = sum(sol_array[1:3, :], dims = 1)
```

@@

lines!(ax, sol.t, sol_array[1, :], linewidth = 3, label = "S(t)")
lines!(ax, sol.t, sol_array[2, :], linewidth = 3, label = "I(t)")
lines!(ax, sol.t, sol_array[3, :], linewidth = 3, label = "R(t)")
lines!(ax, sol.t, sol_array[4, :], linewidth = 3, label = "N(t)")
